Keeping and discarding players

### 2021-02-23 inst/retain.Rmd
clarification

Above, rows of object `jj` correspond to competitors and columns to
judges.  Object `jj` does not function as a rank table because the
entries are not sequential.

@@

>>>>

Above, rows of object `jj` correspond to competitors and columns to
judges.  Object `jj` does not function as a rank table because the
entries are not sequential (judge `J2`, for example, has no
second-ranked competitor).

@@

###  Conclusions{-}

It does not seem possible to take a `hyper2` object and discard
certain players.  It seems that the only way to discard players is to
work with the original observation, discard players in the dataset
according to some criterion, and coerce to a likelihood function.
